\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex
testbed-pic

\author{Paper \# 56, 16 pages}
% \author{Firstname Lastname}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

@@

FFC \cite{FFC} guarantees a total bandwidth from DC1 to DC4 under at most $l$ concurrent node/link failures, and here we simply use $l=1$. Figure \ref{motivatio_fig}(b) shows FFC can support 10Gbps bandwidth from DC1 to DC4 in 99.996\% time even with one failure (the probability that the two paths fail simultaneously is $(1-95.999904\%) \times (1-99.8999001\%) = 0.004004092096\%$). Since user1 and user2 can get respectively 3.34Gbps and 6.66Gbps, which are evenly distributed on the two paths from DC1 to DC4, 
and neither of their bandwidth demands can be satisfied. This shows \textit{FFC does not differentiate between paths with different availabilities.} The lower path has a much smaller failure probability, and it is wasteful without utilizing it as much as possible.

@@

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Bandwidth allocation for DC2$\to$DC4 failure}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Measured and demand ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-public-2.pdf}}
\subfigure[Monetary gain after failures]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/test-bed-profit.pdf}}
\subfigure[Data loss ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-data-loss-2.pdf}}
\caption{A public cloud example: tenants' demands arrive obeying poisson process and the duration of demands are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup}
We build a testbed with 6 servers to emulate a small inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding VM interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4 shortest paths between each source-destination pair as the tunnels in TE algorithms.

@@

\begin{figure*}[t]
\centering
\subfigure[Bandwidth-based availability]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/test.pdf}}
\subfigure[Link failures]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/link-failures.pdf}}
%\subfigure[Scheduled results (SWAN)]{
%\includegraphics[width=0.19\textwidth]{fig/testbed6.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
\subfigure[Data loss ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/data-loss.pdf}}
%\subfigure[After L4 failure ($\mathsf{BATE}$-1)]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/time2.pdf}}
\subfigure[Events after L3 failure]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/fake-failure.pdf}}

\caption{A private cloud example: we deploy three services whose details are shown in Table \ref{testbed-1}.}
\label{e1}
\end{figure*}

\textbf{Evaluations on continuous demand arrivals.}
We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline,OWAN,Teavar}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 minutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes and is repeated for 50 times, 
where link failures occur probabilistically,

@@

\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwith availability requirement can be guaranteed. 
Since we emulate different link failures according to their probabilities in every second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfication, under 
different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands will be much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
To further illustrate the difference in their mechanisms, 
we plot in Figure \ref{e2}(c), for each algorithm, the ratio of the allocated bandwidth 
to the demanded bandwidth. 
The cdf curve shows that FFC is too conservative in bandwidth allocation, 
and fails to allocate proper bandwidth in almost 60\% time.   
On the other hand, although TEAVAR provides bandwidth fairly well, 
it ignores the diverse availability requirements of different users, 
and achieves a lower satisfication ratio than $\mathsf{BATE}$.

\textit{Failure Recovery} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(d) plots the overall profit $\mathsf{BATE}$, FFC and TEAVAR can achieve for admitted demands, under three different admission control strategies, i.e., fixed, BATE-AD (which is the strategy $\mathsf{BATE}$ uses) and optimal. 
\textbf{TBD: This is because $\mathsf{BATE}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.}
Figure \ref{e2}(e) further depicts the fraction of profit loss caused by SLA violations, where the baseline for each algorithm is the profit it can achieve when no failures occur. 
\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
Compared with TEAVAR, FFC has a lower profit loss ratio due to its conservative bandwidth allocation, as indicated in Figure \ref{e2}(c) earlier.

\textbf{TBD: We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{BATE}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, 
while $\mathsf{BATE}$ focuses on Monetary gain rather than data loss.}
%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{BATE}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{BATE}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{BATE}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{BATE}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.

@@

%In this part we will perform experiments on our testbed to evaluate the performance of  $\mathsf{BATE}$.
 \begin{table}
\scriptsize
\centering
\caption{Scheduled results of different schemes.}\label{testbed-1}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|c|l|l|l|l|ll} \hline
\setlength{\tabcolsep}{10pt}
{Service}&\multicolumn{1}{|c|}{paths}&\multicolumn{1}{|c|}{$\mathsf{BATE}$}&\multicolumn{1}{|c|}{TEAVAR}&\multicolumn{1}{|c|}{FFC}\\
\hline
&{DC1$\to$DC2$\to$DC3}&0&500&0\\
{Service-1}&{DC1$\to$DC4$\to$DC3}&1000&500&250\\
(99.5\%)&{DC1$\to$DC2$\to$DC5$\to$DC4$\to$DC3}&0&0&0\\
&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&0&0&0\\
\hline
&{DC1$\to$DC4}&0&250&0\\
{Service-2}&{DC1$\to$DC2$\to$DC5$\to$DC4}&0&0&0\\
(99.9\%)&{DC1$\to$DC2$\to$DC3$\to$DC4}&500&0&250\\
&{DC1$\to$DC6$\to$DC5$\to$DC4}&0&250&250\\
\hline
&{DC1$\to$DC2$\to$DC5}&500&500&750\\
{Service-3}&{DC1$\to$DC4$\to$DC5}&0&250&0\\
(95\%)&{DC1$\to$DC6$\to$DC5}&1000&750&750\\
&{DC1$\to$DC2$\to$DC3$\to$DC4$\to$DC5}&0&0&0\\
%&&&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&{750}\\
%&&&{DC1$\to$DC2$\to$DC3}&{0}\\
%&&&{DC1$\to$DC4$\to$DC3}&{0}\\
%{service-1}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC2$\to$DC3}&{750}\\
%(95\%)&&&{DC1$\to$DC4$\to$DC3}&{750}\\
%&&\multirow{2}{*}{{SWAN}}&{DC1$\to$DC2$\to$DC3}&{1000}\\
%&&&{DC1$\to$DC4$\to$DC3}&{500}\\
%\hline
%&\multirow{6}{*}{500}&\multirow{2}{*}{{$\mathsf{BATE}$}}&{DC1$\to$DC4}&{250}\\
%&&&{DC1$\to$DC2$\to$DC3$\to$DC4}&{250}\\
%{service-2}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC4}&{250}\\
%(99.99\%)&&&{DC1$\to$DC6$\to$DC5$\to$DC4}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC4}&{500}\\
%\hline
%&\multirow{4}{*}{500}&{{$\mathsf{BATE}$}}&{DC1$\to$DC6$\to$DC5}&{500}\\
%{service-3}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC6$\to$DC5}&{250}\\
%(90\%)&&&{DC1$\to$DC2$\to$DC5}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC6$\to$DC5}&{500}\\
\hline
\end{tabular}
\end{table}

\textbf{Evaluations on parallel demands.}
Now we use another example with three user demands to illustrate more details of $\mathsf{BATE}$. 
In our evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
Another factor we must pay attention into is the

>>>>

\author{Paper \# 56, 18 pages}
% \author{Firstname Lastname}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

@@

FFC \cite{FFC} guarantees a total bandwidth from DC1 to DC4 under at most $l$ concurrent node/link failures, and here we simply use $l=1$. Figure \ref{motivatio_fig}(b) shows FFC can support 10Gbps bandwidth from DC1 to DC4 in 99.996\% time even with one failure (the probability that the two paths fail simultaneously is $(1-95.999904\%) \times (1-99.8999001\%) = 0.004004092096\%$. Since user1 and user2 can get respectively 3.34Gbps and 6.66Gbps, which are evenly distributed on the two paths from DC1 to DC4, 
and neither of their bandwidth demands can be satisfied. This shows \textit{FFC does not differentiate between paths with different availabilities.} The lower path has a much smaller failure probability, and it is wasteful without utilizing it as much as possible.

@@

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Pre-compute Backup allocation for link failure on DC2$\to$DC4}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$.}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology. Each link has the same capacity 1Gbps but  different failure probability.}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Bandwidth availability]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Monetary loss after failures]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall monetary gain]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{BA demands arrive with poisson process and their duration are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup}
We build a testbed with 6 servers to emulate a small inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding network interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4 shortest paths between each source-destination pair as the tunnels in TE algorithms.

@@

%

We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 miniutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes and is repeated for 50 times, 
where link failures occur probabilistically,

@@

\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwidth availability requirement can be guaranteed. 
Since we emulate different link failures according to their probabilities in each second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfaction, under  different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands will be much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
%To further illustrate the difference in their mechanisms,

\textit{Failure Recovery.} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(c) depicts the fraction of profit loss caused by SLA violations under three different admission control strategies, i.e., fixed, BATE-AD (which is the strategy $\mathsf{BATE}$ uses) and optimal, where baseline for each algorithm is the profit it can achieve when no failures occur. 
%\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
Compared with TEAVAR, FFC has a lower profit loss ratio due to its conservative bandwidth allocation.

\textit{Overall Profit.}
Figure \ref{e2}(d) plots the overall profit gain comparison among $\mathsf{BATE}$, FFC and TEAVAR  for all arrived demands.
Thanks to the hard guarantee of bandwidth availability and optimization of profit gain after failures, $\mathsf{BATE}$ can maintain at least 15\% more profit than  FFC and TEAVAR.

Due to space limitations, more details of the evaluations are shown in  Appendix \ref{testbed-appendix}.

%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{BATE}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{BATE}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{BATE}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{BATE}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.

@@

%In this part we will perform experiments on our testbed to evaluate the performance of  $\mathsf{BATE}$.
 \begin{table}
\scriptsize
\centering
\caption{Scheduled results of different schemes.}\label{testbed-1}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|c|l|l|l|l|ll} \hline
\setlength{\tabcolsep}{10pt}
{Service}&\multicolumn{1}{|c|}{paths}&\multicolumn{1}{|c|}{$\mathsf{BATE}$}&\multicolumn{1}{|c|}{TEAVAR}&\multicolumn{1}{|c|}{FFC}\\
\hline
&{DC1$\to$DC2$\to$DC3}&0&500&0\\
{demand-1}&{DC1$\to$DC4$\to$DC3}&1000&500&250\\
(99.5\%)&{DC1$\to$DC2$\to$DC5$\to$DC4$\to$DC3}&0&0&0\\
&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&0&0&0\\
\hline
&{DC1$\to$DC4}&0&250&0\\
{demand-2}&{DC1$\to$DC2$\to$DC5$\to$DC4}&0&0&0\\
(99.9\%)&{DC1$\to$DC2$\to$DC3$\to$DC4}&500&0&250\\
&{DC1$\to$DC6$\to$DC5$\to$DC4}&0&250&250\\
\hline
&{DC1$\to$DC2$\to$DC5}&500&500&750\\
{demand-3}&{DC1$\to$DC4$\to$DC5}&0&250&0\\
(95\%)&{DC1$\to$DC6$\to$DC5}&1000&750&750\\
&{DC1$\to$DC2$\to$DC3$\to$DC4$\to$DC5}&0&0&0\\
%&&&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&{750}\\
%&&&{DC1$\to$DC2$\to$DC3}&{0}\\
%&&&{DC1$\to$DC4$\to$DC3}&{0}\\
%{service-1}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC2$\to$DC3}&{750}\\
%(95\%)&&&{DC1$\to$DC4$\to$DC3}&{750}\\
%&&\multirow{2}{*}{{SWAN}}&{DC1$\to$DC2$\to$DC3}&{1000}\\
%&&&{DC1$\to$DC4$\to$DC3}&{500}\\
%\hline
%&\multirow{6}{*}{500}&\multirow{2}{*}{{$\mathsf{BATE}$}}&{DC1$\to$DC4}&{250}\\
%&&&{DC1$\to$DC2$\to$DC3$\to$DC4}&{250}\\
%{service-2}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC4}&{250}\\
%(99.99\%)&&&{DC1$\to$DC6$\to$DC5$\to$DC4}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC4}&{500}\\
%\hline
%&\multirow{4}{*}{500}&{{$\mathsf{BATE}$}}&{DC1$\to$DC6$\to$DC5}&{500}\\
%{service-3}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC6$\to$DC5}&{250}\\
%(90\%)&&&{DC1$\to$DC2$\to$DC5}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC6$\to$DC5}&{500}\\
\hline
\end{tabular}
\end{table}

Now we use another example with three user demands to illustrate more details of $\mathsf{BATE}$. 
In our evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
%Another factor we must pay attention into is the

\begin{figure}
\centering
\subfigure[Bandwidth availability]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/test.pdf}}
\subfigure[Failures of links]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/link-failures.pdf}}
%\subfigure[Scheduled results (SWAN)]{
%\includegraphics[width=0.19\textwidth]{fig/testbed6.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Data loss ratio]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/data-loss.pdf}}
%%\subfigure[After L4 failure ($\mathsf{BATE}$-1)]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/time2.pdf}}
%\subfigure[Events after L3 failure]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/fake-failure.pdf}}
\caption{ An simple example with three user demands whose details are shown in Table \ref{testbed-1}.}
\label{e1}
\end{figure}
